### 2023-05-15 paper/content.tex
Add a function to plot the stereonets
Include a stereonet and a map plot of the simple synthetic to be more
consistent.
Updates from Overleaf

The first synthetic model was performed by generating the vertical magnetic field ($b_z$) derived from a simple set of four dipoles with similar dipole moments amplitudes, but different inclinations and declinations, contaminated by high-frequency noise.
The purpose of this model is to investigate the efficiency of the combination of Euler Deconvolution and the dipole moment inversion, thus being a validation of the methodology.

The second model contains 100 dipoles with different dipole moment magnitudes, having inclinations and declinations around two stable directions.
The magnetic field generated from these sources is corrupted by both low and high-frequency noise.
The complexity of this synthetic data seeks to more faithfully emulate real magnetic microscopy data.

\subsection{Simple simulation: Validating the methodology}

@@

\begin{figure}[tb!]
\centering
\includegraphics[width=0.5\linewidth]{figures/simple-synthetic-dipole-moment.png}
\caption{
Comparison of true and estimated dipole magnetic moments and directions.
}
\label{fig_synthetic_simple_results}
\end{figure}

The positions of each source obtained with Euler Deconvolution were used as an input parameter for the dipole moment inversion.
The estimated inclination ($I$), declination ($D$), and dipole moment amplitude ($m$) are shown in Figure~\ref{fig_synthetic_simple_results} along with the corresponding true values.
Table~\ref{tab_synthetic_simple_results} also shows the true and estimate dipole moments as well as their corresponding standard deviations obtained using Equations~\ref{eq_chi_square}-\ref{eq_variances}.

\begin{table}[tb]
  \begin{center}
    \small
    \input{simple-synthetic-results.tex}
  \end{center}
  \caption{
  True and estimated source positions and dipole moments for the simple synthetic data application.
  Each source positioning and magnetization parameters modeled and recovered by the least square estimator, respectively.}
  \label{tab_synthetic_simple_results}
\end{table}

@@

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{figures/complex-synthetic-data.png}
  \caption{
    Complex synthetic data and the various processing steps performed prior to the dipole moment inversion.
    a) The synthetic high and low-frequency noise-corrupted $b_z$ observations at
    $z = \qty{5}{\micro\meter}$ due to two clusters of stable directions simulated.
    b) Residual anomaly map after the $3^{th}$ degree polynomial signal subtraction and upward-continued data to $z = \qty{10}{\micro\meter}$ to attenuated long and short-wavelength noise, respectively.
    c) The total gradient amplitude (TGA) calculated from the
    upward-continued data, which is able to concentrate the signal on top
    of each dipolar source.
    d) The contrast-stretched TGA, highlighting the signal of all sources, especially the weaker ones.
    e) The detected source bounding boxes (black squares) that correctly
    encapsulate the signal of the sources.
    f) The estimated source locations (colored circles) from Euler
    Deconvolution of the upward-continued data inside each bounding box.
    The color represents the difference between the true and estimated
    $z$ coordinates.
  }
  \label{complex-synthetic-data}
\end{figure}

Since now the data have both high and low-frequency noise, we first fit a $3^{th}$ degree polynomial to the data to remove the low-frequency noise.
We then followed the same processing steps as for the simple synthetic: upward continuation (Figure~\ref{complex-synthetic-data}b),
TGA calculation (Figure~\ref{complex-synthetic-data}c), contrast stretching (Figure~\ref{complex-synthetic-data}d), blob detection (Figure~\ref{complex-synthetic-data}e), and Euler Deconvolution (Figure~\ref{complex-synthetic-data}e).
A total of 99 sources out of the original 103 were successfully detected by our workflow.

@@

Figure~\ref{complex-synthetic-stereograms} shows stereograms with the directions generated by the modeled (Fig.~\ref{complex-synthetic-stereograms}a) and the estimated vectors (Fig.~\ref{complex-synthetic-stereograms}b) for each source. The distribution of the estimated directions is coincident with the true directions aside from a few sources, the same ones with the higher values of direction misfit (Fig.~\ref{complex-synthetic-comparison}a) which is probably associated with the mutual interference of sources close to each other or within the same window. When filtered to include only data with R\textsuperscript{2} \textgreater 0.85 and SNR \textgreater 5 the obtained direction distribution is closer to the true distribution (Fig.~\ref{complex-synthetic-stereograms}c).

@@

After remanence acquisition, we performed a magnetic map with the Quantum
Diamond Microscope (QDM) at Harvard University over a sample section of
approximately $\qty{1410}{\um} \times \qty{2256}{\um}$ (Figure~\ref{real-data}a) with a grid
spacing of \qty{2.35}{\um} and a sensor-sample distance of approximately \qty{5}{\um}, totaling
576,000 data points. The QDM is housed in a shielded room, in
order to avoid the influence of the Earth's magnetic field while the data were taken in projected magnetic microscopy (PMM) mode and converted to the vertical component of magnetic field ($b_z$) using a spectral approach \citep{Lima2009, Fu2020,
Glenn2017}. We applied a bias field of \qty{0.9}{\milli\tesla} during the measurement, which was periodically reversed to result in an effective background field of $< \qty{1}{\micro\tesla}$.  After applying the magnetic anomaly detection algorithm, it was
possible to determine the windows for 75 potential sources
(Figure~\ref{real-data}e).

\begin{figure}[tb!]
\centering
\includegraphics[width=1\linewidth]{figures/real-data.png}
\caption{Real data and the various processing steps performed prior to the dipole moment inversion.
    a) The real sample vertical component magnetic data $b_z$ observations at
    $z = \qty{5}{\um}$.
    b) Residual anomaly map after the $3^{th}$ degree polynomial signal subtraction and upward-continued data to $z = \qty{10}{\um}$ to attenuated long and short-wavelength noise, respectively.
    c) The total gradient amplitude (TGA) calculated from the
    upward-continued data.
    d) The contrast-stretched TGA.
    e) The detected source bounding boxes (black squares) that correctly
    encapsulate the main signal of the sources.
    f) The estimated source locations (colored circles) from Euler
    Deconvolution of the upward-continued data inside each bounding box.
    The color represents the estimated $z$ coordinates.
  }
\label{real-data}
\end{figure}

@@

Since the pioneering work of \cite{Egli2000}, many methodologies were proposed for solving the inverse problem o micromagnetic data, and for purpose of comparison we separate them into two categories based on the main estimated parameter by the inversion procedure.
In the first type of approach, the main goal is usually to estimate average magnetization by inverting the whole sample superficial magnetization data commonly by means of unidirectional problem, uniform directions with non-negative variable dipole moments \citep[e.g.,][]{Weiss2007}, including performance enhancement in the spatial domain \citep[e.g.,][]{Myre2019} or frequency domain  \citep[e.g.,][]{Lima2013}.
This methodology can be used to remarkably estimate the average magnetic direction and the total moment direction with the assumption that the particles were all magnetized in the direction of the same induced field \citep[sIRM and/or NRM in basalts,][]{Weiss2007}.
However, this assumption is not always true when dealing with complex samples (i.e., more than one stable direction), which leads to the same drawbacks as the classic paleomagnetic measurements using bulk samples.
The second type of approach has the goal of finding the individual source magnetic properties, which can be done by either inverting the dipole moment of a single source within a cropped section of an upward continued anomaly map \citep[e.g.,][]{Lima2016, Fu2020} or by the insertion of additional information of the sources’ shape, such as micro-computed tomography (microCT) \citep[e.g.,][]{Fabian2019, DeGroot2018, DeGroot2021}.
The latter further allows unique estimation of magnetic moment configuration of even higher orders components through spherical harmonics expansion constrained by micromagnetic models \citep[e.g.,][]{CortesOrtuno2021, CortesOrtuno2022}.
Such outstanding techniques come with some troubles of having to mechanically select the data for inversion or dealing with the weaknesses of the additional method used.
The MicroCT, for example, is a popular non-destructive technique for high-resolution imaging of the material internal structures, and yet, it is accompanied by some limitations when it comes to paleomagnetic studies: firstly, the technique has a spatial resolution on the order of micrometers, which is not sufficient to directly image the fined grained single-domain magnetite \citep{DeGroot2018}.
The microCT also struggles to discern ferromagnetic (\textit{l.s.}) from non-magnetic/antiferromagnetic minerals, as pointed out by \cite{DeGroot2021}, since they usually have similar densities and therefore similar X-ray attenuation \citep{Cnudde2013}.
In any case, the major limitation of microCT lies in the trade-off between the resolution and the sample size, requiring small sample volumes to achieve higher resolutions causing the technique to be too time-consuming.

@@

The complex synthetic data allows better observation of the strengths and limitations of the windows approach.
The main strengths that can be mentioned are: (i) the applied technique not only detects most of the modeled sources but also (ii) most of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Fig.~\ref{complex-synthetic-comparison}a).
(iii) The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Figure~\ref{complex-synthetic-comparison}b) when $R^2$ and SNR scores are considered high ($\geq 0.85$ and $\geq 5$, respectively) (Figure~\ref{complex-synthetic-comparison}c-d).
(iv) Shallow particles grouped in clusters are usually well individualized during window selection, as well as (v) some isolated particles that produce a weak magnetic signal.
The major limitations observed were: (i) the blob detection fails when there are sources too close, grouping them into the same window, thus causing an erroneous result both for Euler deconvolution and for the magnetic parameters.
(ii) The very same occurs when there is a source under another, in this case, the magnetic signal is the sum of both.
(iii) In clusters of larger and/or deeper particles, although the method individualizes them well, the magnetic signal of the neighboring particles can considerably influence the result of the inversion, especially the estimated dipole moment (cluster in the Figure~\ref{complex-synthetic-comparison}b with the highest misfit values).
As expected, there is a direct relationship between the dipole intensity and depth with the observed errors.
It is clear from the error bars in Figure~\ref{complex-synthetic-comparison} that deep-seated sources and/or particles with small dipole moments generate worse results, essentially because they will produce weaker anomalous fields in the magnetic maps.
Note nonetheless, that even sources with small dipole moments when close to the surface are adequately modeled by our method, because of the trade-off between signal and noise for grains near the sensor.

>>>>

The first synthetic model was performed by generating the vertical magnetic field ($b_z$) derived from a simple set of four dipoles with similar dipole moments amplitudes, but different inclinations and declinations, contaminated by high-frequency noise.
The purpose of this model is to investigate the efficiency of the combination of Euler deconvolution and the dipole moment inversion, thus being a validation of the methodology.

The second model simulates a hundred sources with both dipolar and non-dipolar magnetic components and their vertical magnetic field ($b_z$) at different height levels, also corrupted with high-frequency noise. This section is carried out in order to assess the ability of the algorithm to deal with sources with strong non-dipolar components.

The third model contains 103 dipoles with different dipole moment magnitudes, having inclinations and declinations around two stable directions.
The magnetic field generated from these sources is corrupted by both low and high-frequency noise.
The complexity of this synthetic data seeks to more faithfully emulate real magnetic microscopy data.

\subsection{Simple simulation: Validating the methodology for dipolar sources}

@@

\begin{figure}[tb!]
\centering
\includegraphics[width=\linewidth]{figures/simple-synthetic-dipole-moment.png}
\caption{
Comparison of true and estimated dipole magnetic moments and directions.
}
\label{fig_synthetic_simple_results}
\end{figure}

The positions of each source obtained with Euler deconvolution were used as an input parameter for the dipole moment inversion.
The estimated inclination ($I$), declination ($D$), and dipole moment amplitude ($m$) are shown in Figure~\ref{fig_synthetic_simple_results} along with the corresponding true values.
Table~\ref{tab_synthetic_simple_results} also shows the true and estimate dipole moments as well as their corresponding standard deviations obtained using Equations~\ref{eq_chi_square}-\ref{eq_variances}.

\begin{table}[tb]
  \begin{center}
    \small
    \input{simple-synthetic-results.tex}
  \end{center}
  \caption{
  True and estimated source positions and dipole moments for the simple synthetic data application.
  Each source modeled and recovered positioning and magnetization parameters by the least square estimator, respectively.}
  \label{tab_synthetic_simple_results}
\end{table}

\subsection{Simple simulation: Validating the methodology for non-dipolar sources}

Typically, when conducting magnetic field measurements with a large distance between the sensor and the magnetic anomaly source, higher-order non-dipole magnetization components such as quadrupoles and octupoles are disregarded. However, in magnetic microscopy, where the sensor is positioned very close to the sample, these higher-order components might be detected. This phenomenon is observed in paleomagnetic studies on particles with a PSD domain state, where magnetization is non-uniform throughout the grain. To assess the magnetic signal attenuation, simulations were conducted on particles with more complex magnetization at varying distances from the sensor.

To simulate particles with non-dipole magnetization components, we specified a spherical volume with a radius of about 1 $\mu$m. Within this volume, we added 200 dipolar point particles with varying magnetization directions and magnetic moments. These directions were generated randomly to follow a normal distribution centered on the direction Dec=90°/Inc=0°, with a magnetic moment of $10^{-14}$ Am$^2$. We also randomly generated the spatial positions around a central position of $x_c=25~\mu$m, $y_c=25~\mu$m, and $z_c=\alpha~\mu$m, where $\alpha$ = 0, 1, ... 11 corresponds to the variation in depth of the particle. By summing the $m_x$, $m_y$, and $m_z$ components of each modeled particle, we obtained the Cartesian magnetization components for the spherical particle. The centroid of the particle was defined by the average of the $x_c$, $y_c$, and $z_c$ positions. The modeled vertical magnetic field was corrupted by a random noise of mean zero and a standard deviation of 20 nT.

According to Figure~\ref{non-dipolarity-synthetic-data} obtained from this simulation, it can be observed that when the particle is very close to the sensor, there is a strong non-dipolar contribution (Figure~\ref{non-dipolarity-synthetic-data}a-b) characterized by low $R^2$ values, indicating low dipolarity. As the distance increases, the magnetic signal is strongly attenuated, especially the non-dipolar components that decay more rapidly than the dipolar component, resulting in a rapid increase in $R^2$ (Figure~\ref{non-dipolarity-synthetic-data}c-d). At distances above 5 $\mu$m, there is practically only the contribution of the dipolar component, causing $R^2$ values to be very close to 1 (Figure~\ref{non-dipolarity-synthetic-data}e-f).

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{paper/figures/non-dipolarity-synthetic.png}
  \caption{Caption: Simulated magnetic microscopy data for a spherical source with both dipolar and non-dipolar magnetic components. The distance from the sensor varies from 1 µm to 6 µm (a-f).}
  \label{non-dipolarity-synthetic-data}
\end{figure}

To assess the algorithm's capability to handle particles with more complex magnetization, we replicated the particle generation procedure 100 times with variations in the randomness of magnetization and point particle positions. Subsequently, the Cartesian position of the spherical particle was estimated using ED, and the magnetization parameters were determined by inverting the magnetic field data. The effectiveness of position recovery was measured by comparing the particle's centroid with the solution of the Euler equation for $x_c$, $y_c$, and $z_c$ (Figure~\ref{non-dipolarity-synthetic-data-positioning}a, b, and c, respectively). As shown in Figure~\ref{non-dipolarity-synthetic-data-positioning}, ED estimates the positions of particles with more complex magnetization well, especially for sensor-source distances greater than 5 µm, where the median of the distributions is centered at zero. However, when the sensor-source distance is small enough for there to be a strong contribution from higher-order components, a lower degree of dipolarity is observed, expressed as lower values of $R^2$ (Figure~\ref{non-dipolarity-synthetic-data-inversion}a). Consequently, in these cases, there are higher errors in the direction of magnetization (Figure~\ref{non-dipolarity-synthetic-data-inversion}b) and in the magnetic moment's intensity (Figure~\ref{non-dipolarity-synthetic-data-inversion}c), which was expected since the inversion considers only the dipolar component. However, dipolarity significantly increases as the sensor distance increases, while errors in direction and magnetic moment decrease significantly (Figure~\ref{non-dipolarity-synthetic-data-inversion}).

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{paper/figures/non-dipolarity-synthetic-positioning.png}
  \caption{The simulation was randomly replicated (N=100) to test the effectiveness of the Euler deconvolution in estimating the position of the modeled particles. The difference between the true position (centroid) and the estimated position was calculated for each replicate and plotted as a boxplot. The boxplot shows the distribution of differences in the (a) $x_c$, (b) $y_c$, and (c) $z_c$.}
  \label{non-dipolarity-synthetic-data-positioning}
\end{figure}

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{paper/figures/non-dipolarity-synthetic-inversion.png}
  \caption{The simulation was randomly replicated (N=100) to assess the accuracy of the algorithm in recovering the magnetic direction and moment of the modeled particles. The goodness of fit was measured by the R-squared value (a), while the angular error (b) and intensity error (c) between the real and modeled magnetic vector were plotted in degrees and percentages ($|100 \left( m_{true} - m_{estimated}\right) ~/~ m_{true}|$), respectively.}
  \label{non-dipolarity-synthetic-data-inversion}
\end{figure}

@@

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{figures/complex-synthetic-data.png}
  \caption{
    Complex synthetic data and the various processing steps performed prior to the dipole moment inversion.
    a) The synthetic high and low-frequency noise-corrupted $b_z$ observations at
    $z = \qty{5}{\micro\meter}$ due to two clusters of stable directions simulated.
    b) Anomaly map after the upward-continued data to $z = \qty{10}{\micro\meter}$ to attenuated long and short-wavelength noise.
    c) The total gradient amplitude (TGA) calculated from the
    upward-continued data, which is able to concentrate the signal on top
    of each dipolar source.
    d) The contrast-stretched TGA, highlighting the signal of all sources, especially the weaker ones.
    e) The detected source bounding boxes (black squares) that correctly
    encapsulate the signal of the sources.
    f) The estimated source locations (colored circles) from Euler
    Deconvolution of the upward-continued data inside each bounding box.
    The color represents the difference between the true and estimated
    $z$ coordinates.
  }
  \label{complex-synthetic-data}
\end{figure}

We then followed the same processing steps as for the simple synthetic: upward continuation (Figure~\ref{complex-synthetic-data}b),
TGA calculation (Figure~\ref{complex-synthetic-data}c), contrast stretching (Figure~\ref{complex-synthetic-data}d), blob detection (Figure~\ref{complex-synthetic-data}e), and Euler Deconvolution (Figure~\ref{complex-synthetic-data}e).
A total of 99 sources out of the original 103 were successfully detected by our workflow.

@@

Figure~\ref{complex-synthetic-stereograms} shows stereograms with the directions generated by the modeled (Figure~\ref{complex-synthetic-stereograms}a) and the estimated vectors (Figure~\ref{complex-synthetic-stereograms}b) for each source. The distribution of the estimated directions is coincident with the true directions aside from a few sources, the same ones with the higher values of direction misfit (Figure~\ref{complex-synthetic-comparison}a) which is probably associated with the mutual interference of sources close to each other or within the same window. When filtered to include only data with R\textsuperscript{2} \textgreater 0.85 and SNR \textgreater 5 the obtained direction distribution is closer to the true distribution (Figure~\ref{complex-synthetic-stereograms}c).

@@

After remanence acquisition, we performed a magnetic map with the Quantum
Diamond Microscope (QDM) at Harvard University over a sample section of
approximately $\qty{1410}{\um} \times \qty{2256}{\um}$ (Figure~\ref{real-data}a) with a grid
spacing of \qty{2.35}{\um} and a sensor-sample distance of approximately \qty{5}{\um}, totaling
576,000 data points. The QDM is housed in a shielded room, in
order to avoid the influence of the Earth's magnetic field while the data were taken in projected magnetic microscopy (PMM) mode and converted to the vertical component of magnetic field ($b_z$) using a spectral approach \citep{Lima2009, Fu2020,
Glenn2017}. We applied a bias field of \qty{0.9}{\milli\tesla} during the measurement, which was periodically reversed to result in an effective background field of $< \qty{1}{\micro\tesla}$.  After applying the magnetic anomaly detection algorithm (Figure~\ref{real-data}b-e), it was
possible to determine the windows for 75 potential sources, as shown in Figure~\ref{real-data}e.

\begin{figure}[tb!]
\centering
\includegraphics[width=1\linewidth]{figures/real-data.png}
\caption{Real data and the various processing steps performed prior to the dipole moment inversion.
    a) The real sample vertical component magnetic data $b_z$ observations at
    $z = \qty{5}{\um}$.
    b) Anomaly map after the upward-continued data to $z = \qty{10}{\um}$ to attenuated long and short-wavelength noise.
    c) The total gradient amplitude (TGA) calculated from the
    upward-continued data.
    d) The contrast-stretched TGA.
    e) The detected source bounding boxes (black squares) that correctly
    encapsulate the main signal of the sources.
    f) The estimated source locations (colored circles) from Euler
    Deconvolution of the upward-continued data inside each bounding box.
    The color represents the estimated $z$ coordinates.
  }
\label{real-data}
\end{figure}

@@

Since the pioneering work of \cite{Egli2000}, many methodologies were proposed for solving the inverse problem o micromagnetic data, and for the purpose of comparison we separate them into two categories based on the main estimated parameter by the inversion procedure.
In the first type of approach, the main goal is usually to estimate average magnetization by inverting the whole sample superficial magnetization data commonly by means of unidirectional problem, uniform directions with non-negative variable dipole moments \citep[e.g.,][]{Weiss2007}, including performance enhancement in the spatial domain \citep[e.g.,][]{Myre2019} or frequency domain  \citep[e.g.,][]{Lima2013}.
This methodology can be used to remarkably estimate the average magnetic direction and the total moment direction with the assumption that the particles were all magnetized in the direction of the same induced field \citep[sIRM and/or NRM in basalts,][]{Weiss2007}.
However, this assumption is not always true when dealing with complex samples (i.e., more than one stable direction), which leads to the same drawbacks as the classic paleomagnetic measurements using bulk samples.
The second type of approach has the goal of finding the individual source magnetic properties, which can be done by either inverting the dipole moment of a single source within a cropped section of an upward continued anomaly map \citep[e.g.,][]{Lima2016, Fu2020} or by the insertion of additional information of the sources’ shape, such as micro-computed tomography (microCT) \citep[e.g.,][]{Fabian2019, DeGroot2018, DeGroot2021}.
The latter further allows unique estimation of magnetic moment configuration of even higher orders components through spherical harmonics expansion constrained by micromagnetic models \citep[e.g.,][]{CortesOrtuno2021, CortesOrtuno2022}.
Such outstanding techniques come with some troubles of having to mechanically select the data for inversion or dealing with the weaknesses of the additional method used.
The MicroCT, for example, is a popular non-destructive technique for high-resolution imaging of the material internal structures, and yet, it is accompanied by some limitations when it comes to paleomagnetic studies: firstly, the technique has a spatial resolution on the order of micrometers, which is not sufficient to directly image the fined grained single-domain magnetite \citep{DeGroot2018}.
The microCT also struggles to discern ferromagnetic (\textit{l.s.}) from non-magnetic/antiferromagnetic minerals, as pointed out by \cite{DeGroot2021}, since they usually have similar densities and therefore similar X-ray attenuation \citep{Cnudde2013}.
In any case, the major limitation of microCT lies in the trade-off between the resolution and the sample size, requiring small sample volumes to achieve higher resolutions causing the technique to be too time-consuming.

@@

The complex synthetic data allows better observation of the strengths and limitations of the windows approach.
The main strengths that can be mentioned are: (i) the applied technique not only detects most of the modeled sources but also (ii) most of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Figure~\ref{complex-synthetic-comparison}a).
(iii) The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Figure~\ref{complex-synthetic-comparison}b) when $R^2$ and SNR scores are considered high ($\geq 0.85$ and $\geq 5$, respectively) (Figure~\ref{complex-synthetic-comparison}c-d).
(iv) Shallow particles grouped in clusters are usually well individualized during window selection, as well as (v) some isolated particles that produce a weak magnetic signal.
The major limitations observed were: (i) the blob detection fails when there are sources too close, grouping them into the same window, thus causing an erroneous result both for Euler deconvolution and for the magnetic parameters.
(ii) The very same occurs when there is a source under another, in this case, the magnetic signal is the sum of both.
(iii) In clusters of larger and/or deeper particles, although the method individualizes them well, the magnetic signal of the neighboring particles can considerably influence the result of the inversion, especially the estimated dipole moment (cluster in the Figure~\ref{complex-synthetic-comparison}b with the highest misfit values).
As expected, there is a direct relationship between the dipole intensity and depth with the observed errors.
It is clear from the error bars in Figure~\ref{complex-synthetic-comparison} that deep-seated sources and/or particles with small dipole moments generate worse results, essentially because they will produce weaker anomalous fields in the magnetic maps.
Note nonetheless, that even sources with small dipole moments when close to the surface are adequately modeled by our method, because of the trade-off between signal and noise for grains near the sensor.
